\section{Validation Protocol}
\label{sec:validation}

Validation asks whether the constructed data changes downstream behavior in the intended direction and whether the workflow prevents premature acceptance when regressions appear. The protocol uses LoRA fine-tuning \cite{hu2021lora} on \qwenedit{} as a downstream probe; the Qwen-Image technical report and \qwenedit{} model card document the underlying image-editing backbone used in this probe \cite{wu2025qwenimage,qwen2025qwenimageedit2511}. The report does not claim a new LoRA method; LoRA is used as an instrument for measuring whether the data engine produces useful supervision. We compare against the unadapted base model and a public multi-angle LoRA released by fal \cite{fal2026qwenmultianglelora}, while treating these as external baselines rather than controlled same-recipe data ablations.

Before introducing external feedback, the rotation probe went through a sequence of non-feedback ablations. These runs are named in the text by their design role, with the original internal experiment identifiers kept only in parentheses. The progression matters because the final non-feedback checkpoint is not an arbitrary run: it is the endpoint of a controlled engineering path from a basic RGB rotation LoRA to a stable object-aware prompt interface.

\begin{table}[t]
\centering
\small
\caption{Ablation path from early rotation probes to the first feedback-guided scaling round. The table gives reader-facing names for the original internal experiment identifiers.}
\label{tab:experiment-evolution}
\begin{tabularx}{\linewidth}{l l X}
\toprule
Internal ID & Reader-facing name & Main intervention and role \\
\midrule
exp1 & RGB Rotation LoRA & Initial feasibility probe using dark RGB renders, no explicit direction word, and no object localization. \\
exp3 & Target-Localized BBox LoRA & Adds visual target localization through bounding-box conditioning; useful for diagnosis, but not a clean final interface. \\
exp4 & \brightprobe{} & Fixes raw image inputs, brightens rendering, and adds clockwise direction wording; strongest non-feedback quantitative baseline. \\
exp5 & \semanticprobe{} & Replaces the visual bbox dependency with object-description prompts; comparable to the bright directional probe and cleaner as a deployable non-feedback baseline. \\
R1 & \feedbackprobe{} R1 & Uses external per-angle evaluation to add 20 train-only objects and 60 weak-angle pairs to the semantic-object prompt baseline. \\
\bottomrule
\end{tabularx}
\end{table}

The \semanticprobe{} baseline is the comparison point for the first feedback-guided scaling round because the feedback-loop state uses the object-info prompt checkpoint. Although \brightprobe{} achieves the strongest pixel-level non-feedback score, the object-aware prompt variant provides a cleaner and more deployable baseline: it removes the need for visual bbox overlays while preserving comparable external-benchmark performance. The semantic baseline and the feedback-guided round follow the pair schema and object-disjoint split described above. The object split is frozen across rounds so that changes in validation or benchmark behavior can be attributed to the training-data intervention rather than to leakage or split drift.

The tracked training probe uses rank 32, learning rate \(1\times10^{-4}\), 30 training epochs, and the epoch 29 checkpoint for comparison. The prompt format follows the train-ready instruction field, using view-language instructions that ask the model to rotate an object from the front view to a target side or back view. These settings are reported for reproducibility, but the main claim remains about data construction and diagnosis.

\begin{table}[t]
\centering
\small
\caption{Validation configurations. Feedback-Guided Scaling R1 changes only the train set; validation and test splits remain fixed and object-disjoint.}
\label{tab:dataset-stats}
\input{tables/generated/dataset_stats_booktabs}
\end{table}

The external evaluation uses \spatialedit{} \cite{xiao2026spatialedit} with 488 rotation pairs across 61 objects and eight angle slots. Metrics cover pixel fidelity with PSNR, structural similarity with SSIM, perceptual distance with LPIPS, semantic image similarity with CLIP-I, representation similarity with DINO, distribution-level quality with FID, and VLM-based view and consistency judgments with \scoreview{}, \scorecons{}, and VIE Overall. The use of VLM-based scoring is related to recent visual-instruction evaluation work such as VIEScore \cite{ku2024viescore}. For angle-slot reporting, this report follows the project comparison mapping from indices 0..7 to 45, 90, 135, 180, 225, 270, 315, and 360 degrees.
